\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Full Stack Rust Rewrite Loading}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
i love leptos so this app will be my way to become cracked at rust. it's in
different 
\textcolor{blue}{\href{https://github.com/iturner72/thenetworktimes}{git repo}}
btw (too lazy to update readme in other repo)

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bounty Submission for Balajis on Farcaster}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

balaji put out a
\textcolor{purple}{\href{https://warpcast.com/balajis.eth/0x218b92a7}{cast}} on
wednesday the 6th challenging anyone to create an AI NYT. he provided a nice
example of something working
\textcolor{blue}{\href{https://twitter.com/balajis/status/1601398685106991105?s=46}{18
months ago}} with inferior LLM models. i've been looking for a reason to stay up
all night coding, so i figured i'd give it a shot.


\subsection*{Why \LaTeX\ Ian?}
great question anon! i write these notes everyday at work and on other projects
since pmarca gave me the idea with his anti-todo list concept. blog is no longer
on the internet or else i would link it here. this may be completely useless to
people, but i don't really but much detail in my git commits (i should start) so
maybe this will help if you end up contributing.

\subsubsection*{p.s.}
weeks are in reverse chronological order btw (and the weeks are not sequential,
nor are they full weeks). i'll add a TOC eventually...
