\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Week 14}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Thursday, 8/01/2024}
\begin{itemize}
    \item damn i need to commit more here!
    \item working on cast list and cast entry merging finally. implemented very
        lazy lazy loading. i still don't have shuttle postgres thing set up so i
        have to make all these fetches randomly, so i'd like to keep them to a
        minimum for user data.
    \item this lazy load feature was fun since it gave me an excuse to use some
        \texttt{web_sys} stuff related to interactive observers.
    \item i basically have it so that only the first 8 cast entries load data
        immediately (user data, not cast body), and the rest are loaded as they
        become visible in the viewport.
    \item this was a breeze with this fine grained readtivity business honestly!
    \item the IntersectionObserver types are cracked since i can set a threshold
        for visibility (i used 10 percent in this feature). 
\end{itemize}

\subsection*{Saturday, 8/03/2024}
\begin{itemize}
    \item working on
        \textcolor{blue}{\href{https://github.com/iturner72/thenetworktimes/issues/3}{issue
        3}} and realized that \texttt{create_server_action} seemed interesting
        but not needed since it works well with an ActionForm and i don't really
        need one at the moment. it's nice to know that it's easy enough to add
        though later for like a tweetdeck style fetch.
    \item added images, will wait on reactions until i can get cast creation 
        working i think.
\end{itemize}

\subsection*{Sunday, 8/04/2024}
\begin{itemize}
    \item working on the pfp page and will continue to issue max  
        \textcolor{blue}{\href{https://github.com/iturner72/thenetworktimes/issues/4}{issue 4}}
    \item will study leptos routes since rn things are just really shitty and
        not organized.
    \item oh it's just \texttt{:id} for the path in the route i can use for
        profile, very nice.
    \item i decided to use \texttt{create_memo} for the fid on the profile page
        which uses a params map as a prop, this allows flexibility later i
        think...
    \item either way, i needed to handle the \texttt{ServerFnError} manually in
        the create resourse call for \texttt{user_data}, i should probably use
        the leptos helper libs in the ecosystem, but i feel like doing all these
        annoying manual things helps me learn what the framework is actually
        doing, so i don't mind the extra dev time.
    \item ...
\end{itemize}
