\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Week 16}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Saturday, 8/17/2024}
\begin{itemize}
    \item trying to add redis cache for user data in cast entry; getting molly
        wopped (?) by the borrow checker currently.
    \item okay it's compiling now, but i'm using it improperly.
    \item okay it's working as designed now lets gooo!
    \item i am going to leave the remote feature branches up since i reference
        them in issues, and will help contributors if that ever is a thing.
\end{itemize}

\subsection*{Sunday, 8/18/2024}
\begin{itemize}
    \item that was really easy to get working, but it literally conflicts with
        my lazy loading logic which was based on the user scrolling (before
        caching was implemented) so this clearly breaks things.
    \item i'll need to try to get some sort of client side cache working as
        well, it might be a RIP to the wasm bundle size but oh well, perhaps the
        bundle splitting lads will fix by the time i have a usable app.
    \item omg that was also very easy, now first load on any feed is unusable!!!
        but every subsequent load is lightning which is exactly what i expected
        to happen.
    \item luckily my website is a nice LLM enjoyer, crypto adjacent power app
        that has a questionable use case! :)
    \item again, all these hacks are fun to implement, but really, i should be
        migrating to leptos 0.7 beta since it allows axum to actually do work in
        paralled (i think), in 0.6, even the server functions somehow only run
        blocking on 1 thread if i am not mistaken.
    \item much to do, after 0.7 migration, think about postgres rust shuttle
        like service implementation (rip).
\end{itemize}

