\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Week 18}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Monday, 9/09/2024}
\begin{itemize}
    \item shit i need to grind harder what am i doing.
    \item anyways, let's try to deploy leptos brypto blogs now, server is just
        down hahaha have not pointed domain back to old vercel one.
    \item okay, fr, fundementally i never understood what \texttt{cargo leptos
        watch} (from the  
        \textcolor{blue}{\href{https://github.com/leptos-rs/cargo-leptos}{cargo leptos}}
        build tool) was doing.
    \item i would do a few release build just to test the compile times, but i
        never did anything more.
    \item looking at the fly io deployment example from the book, i simply
        forgot to incorporate the tailwind build step and thought it would just
        magically work somehow. luckily i can just run the help command or read
        the examples.
    \item wow... i've many skill issues related to nginx!!!
    \item much to think about.
\end{itemize}

\subsection*{Tuesday, 9/10/2024}
\begin{itemize}
    \item hard stuck on deploying leptos 0.6 app and migrating to 0.7, so i'll
        just work on features that should work either way.
    \item should brain dump some github issues soon... there is much to do (not 
        in a rush obvi or i wouldn't be using leptos at all)
\end{itemize}

\subsection*{Wednesday, 9/11/2024}
\begin{itemize}
    \item going to work on new thread feature and diesel cli annoyances
    \item let's goo, new thread button working with uuids, diesel cli annoyances
        were not addressed, however haha.
    \item never forget btw
\end{itemize}

\subsection*{Thursday, 9/12/2024}
\begin{itemize}
    \item i really need to properly use the ServerFnError this is getting silly
        lmao, enums are working but i am likely doing far too much work and
        re-implementing things that diesel or leptos provide.
\end{itemize}

\subsection*{Friday, 9/13/2024}
\begin{itemize}
    \item going to try to deploy the minimal darn leptos brypto blogs app yet
        again to prac. i am so bad!
    \item ...
\end{itemize}
